When, why, and how to avoid, prefer, or tolerate inbreeding

### 2018-02-26 presentation/inbreeding.Rmd
Sketch out some introductory slides

@@

@@

@@

Ds    <- observeEvent(input$mate, {
        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
            gen$dat$ID   <- initialise_inds(N = 8);
            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
        }else{
            gen$dat  <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
                                Kf = 40, Km = 40, beta = input$ID, 
                                imm = input$Imm, cost = input$cost, 
                                mu = input$mu);
            iter$all <- c(iter$all, mean(gen$dat$ID[,11:20]));
            iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
            kvalues  <- gen$dat$Rmat;
            kvalues  <- kvalues[,-1];
            if(dim(kvalues)[1] > 80){
                kvalues <- kvalues[1:80, 1:80];
            }
            diag(kvalues) <- NA ;#diag(kvalues) * 0.5;
            iter$kva <- kvalues;
            iter$mkv <- c(iter$mkv, mean(kvalues, na.rm = TRUE));
            mtID     <- gen$dat$last_gen;
            mtt$dat  <- mate_connect(mtID);
        }
})

@@

## Inbreeding tolerance

@@

Ds    <- observeEvent(input$mate3, {
        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
            gen$dat$ID   <- initialise_inds(N = 8);
            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
        }else{
            gen$dat  <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
                                Kf = 40, Km = 40, beta = input$ID3, 
                                imm = input$Imm3, cost = input$cost3, 
                                mu = input$mu3);
            iter$all <- c(iter$all, mean(gen$dat$ID[,11:20]));
            iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
            kvalues  <- gen$dat$Rmat;
            kvalues  <- kvalues[,-1];
            if(dim(kvalues)[1] > 80){
                kvalues <- kvalues[1:80, 1:80];
            }
            diag(kvalues) <- NA ;#diag(kvalues) * 0.5;
            iter$kva <- kvalues;
            iter$mkv <- c(iter$mkv, mean(kvalues, na.rm = TRUE));
        }
})

@@

## More tolerance

@@

Ds    <- observeEvent(input$mate2, {
        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
            gen$dat$ID   <- initialise_inds(N = 8);
            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
        }else{
            gen$dat  <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
                                Kf = 40, Km = 40, beta = input$ID2, 
                                imm = input$Imm2, cost = input$cost2, 
                                mu = input$mu2);
            iter$all <- c(iter$all, mean(gen$dat$ID[,11:20]));
            iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
            kvalues  <- gen$dat$Rmat;
            kvalues  <- kvalues[,-1];
            if(dim(kvalues)[1] > 80){
                kvalues <- kvalues[1:80, 1:80];
            }
            diag(kvalues) <- NA ;#diag(kvalues) * 0.5;
            iter$kva <- kvalues;
            iter$mkv <- c(iter$mkv, mean(kvalues, na.rm = TRUE));
        }
})

@@

## Inbreeding avoidance

## Inbreeding preference

## Parker's model

>>>>

<style>
div.footnotes {
  position: absolute;
  bottom: 0;
  margin-bottom: 10px;
  width: 80%;
  font-size: 0.6em;
}
</style>

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.1.1/jquery.min.js"></script>

<script>
  $(document).ready(function() {
    $('slide:not(.backdrop):not(.title-slide)').append('<div class=\"footnotes\">');

    $('footnote').each(function(index) {
      var text  = $(this).html();
      var fnNum = (index+1).toString().sup();
      $(this).html(text + fnNum);

      var footnote   = fnNum + ': ' + $(this).attr('content') + '<br/>';
      var oldContent = $(this).parents('slide').children('div.footnotes').html();
      var newContent = oldContent + footnote;
      $(this).parents('slide').children('div.footnotes').html(newContent);
    });
  });
</script>

@@

## Inbreeding

- Define relatedness

@@

- What inbreeding depression is, exactly.

- What are the consequences of inbreeding depression.

## Inbreeding behaviour

- What do we exect to see given inbreeding depression?

- inbreeding avoidance
- inbreeding preference
- inbreeding tolerance

## Inbreeding theory

Describe Parker's model

- Resource and mate limited sexes
- Mate encounter, opportunity to outbreed assumed

## Inbreeding theory

<div class = "columns-2">

```{r echo = FALSE, fig.height = 4, fig.width = 5}
inputPanel(
  sliderInput("rr", label = "Relatedness", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.05), 
  sliderInput("dd", label = "Inbreeding Depression", width="100%",
              min = 0.0, max = 1, value = 0, step = 0.1)
)
par(bg = 'transparent', mar = c(0.5, 0.5, 0.5, 0.5));
plot(x = 1:10, y = 1:10, xaxt = "n", yaxt = "n", xlab = "", ylab = "");
# Add see-saw function here to animate the balance
```

<br><br>

- Parker's model
- Add a see-saw plot that weighs relatedness versus inbreeding depression

$$\frac{n}{2} (1 + r)(1 - \delta) > \frac{n}{2}$$

Is inclusive fitness from inbreeding (left) greater than inclusive fitness from outbreeding?

$$\delta < \frac{r}{1+r}$$

</div>

## Interpreting Parker's model

Some key takeaways:

- Inbreeding avoidance is predicted given a sufficiently high threshold of inbreeding depression
- Inbreeding depression thresholds differ between females and males causing sexual conflict
- Females should prefer inbreeding below their inbreeding depression threshold (resource limited) <footnote content="The first awesoem footnote!">here</footnote>:
- Males should *tolerate* inbreeding below their threshold, but *never prefer* (sis will be fine)

@@

Ds    <- observeEvent(input$mate, {
        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
            gen$dat$ID   <- initialise_inds(N = 80);
            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
        }else{
            gen$dat  <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
                                Kf = 40, Km = 40, beta = input$ID, 
                                imm = input$Imm, cost = input$cost, 
                                mu = input$mu);
            iter$all <- c(iter$all, mean(gen$dat$ID[,11:20]));
            iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
            kvalues  <- gen$dat$Rmat;
            kvalues  <- kvalues[,-1];
            if(dim(kvalues)[1] > 80){
                kvalues <- kvalues[1:80, 1:80];
            }
            diag(kvalues) <- NA ;#diag(kvalues) * 0.5;
            iter$kva <- kvalues;
            iter$mkv <- c(iter$mkv, mean(kvalues, na.rm = TRUE));
            mtID     <- gen$dat$last_gen;
            mtt$dat  <- mate_connect(mtID);
        }
})

@@

@@

Ds    <- observeEvent(input$mate3, {
        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
            gen$dat$ID   <- initialise_inds(N = 80);
            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
        }else{
            gen$dat  <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
                                Kf = 40, Km = 40, beta = input$ID3, 
                                imm = input$Imm3, cost = input$cost3, 
                                mu = input$mu3);
            iter$all <- c(iter$all, mean(gen$dat$ID[,11:20]));
            iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
            kvalues  <- gen$dat$Rmat;
            kvalues  <- kvalues[,-1];
            if(dim(kvalues)[1] > 80){
                kvalues <- kvalues[1:80, 1:80];
            }
            diag(kvalues) <- NA ;#diag(kvalues) * 0.5;
            iter$kva <- kvalues;
            iter$mkv <- c(iter$mkv, mean(kvalues, na.rm = TRUE));
        }
})

@@

@@

Ds    <- observeEvent(input$mate2, {
        if( is.null(gen$dat$ID) == TRUE | is.null(gen$dat$ID) == TRUE){
            gen$dat$ID   <- initialise_inds(N = 80);
            gen$dat$Rmat <- initialise_Rmat(gen$dat$ID);
        }else{
            gen$dat  <- new_gen(ID = gen$dat$ID, Rmat = gen$dat$Rmat, 
                                Kf = 40, Km = 40, beta = input$ID2, 
                                imm = input$Imm2, cost = input$cost2, 
                                mu = input$mu2);
            iter$all <- c(iter$all, mean(gen$dat$ID[,11:20]));
            iter$nue <- c(iter$nue, mean(gen$dat$ID[,21:30]));
            kvalues  <- gen$dat$Rmat;
            kvalues  <- kvalues[,-1];
            if(dim(kvalues)[1] > 80){
                kvalues <- kvalues[1:80, 1:80];
            }
            diag(kvalues) <- NA ;#diag(kvalues) * 0.5;
            iter$kva <- kvalues;
            iter$mkv <- c(iter$mkv, mean(kvalues, na.rm = TRUE));
        }
})

@@
